Two Mode Networks and Relational Similarity

### 2023-08-30 analysis.qmd
Updated plots

# Analysis
```{r}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- CA(A, graph = FALSE)
   c <- round(a$CA.res$u[, 2], 3)
   d <- round(b$row$coord[, 1], 3)
   e <- data.frame(c, d)
   ggscatter(e, x = "c", y = "d", label = rownames(A), repel = TRUE)
```

```{r Reflections Bump Charts}
   evens <- function(x) subset(x, x %% 2 == 0)
   odds <- function(x) subset(x, x %% 2 != 0)
   a <- reflections(A, iter = 26)
   p.e.r <- a$p.r[, evens(1:20)]
   p.o.r <- a$p.r[, odds(1:20)]
   p.o.r <- p.o.r[, -1]
   b <- ref.long.dat(a = a$p.r, b = a$g.r, max.iter = 26)
   plot.dat <- b$person$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = person))
   # geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 0.8)
   p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = person), 
                                    size = 4, nudge_x = -3)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 22), 
                              aes(x = n.iter, label = person), 
                              size = 4, nudge_x = 0.5)

@@

```{r Comparative scatters}
   library(Matrix)
   library(FactoMineR)
   AAt <- A %*% t(A)
   AtA <- t(A) %*% A
   bon.res.r <- svd(AAt)$u[, 1]
   bon.res.c <- svd(AtA)$u[, 1]
   names(bon.res.r) <- rownames(A)
   names(bon.res.c) <- colnames(A)
   van.res.r <- TwoModeCA(A)$eigvec.r[, 1]
   van.res.c <- TwoModeCA(A)$eigvec.c[, 1]
   ref.res.r <- scale(reflections(A, iter = 30)$p.r[, 26])
   ref.res.c <- scale(reflections(A, iter = 30)$p.c[, 26])
   ca.res.r <- CA(A, graph = FALSE)$row$coord[, 1]
   ca.res.c <- CA(A, graph = FALSE)$col$coord[, 1]
   dat.r <- data.frame(cbind(a = bon.res.r, b = van.res.r, 
                  c = as.vector(ref.res.r), d = ca.res.r))

```

```{r Main Plot}
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 3, d.r = 12, d.c = 12)
    a <- tmCA.res$A.plot + theme(axis.text.x = element_text(angle = 0, 
                                                            size = 9,
                                                            vjust = -3))
    b <- tmCA.res$corr.plot
    c <- tmCA.res$sim.plot.r
    d <- tmCA.res$sim.plot.c + theme(axis.text.x = element_text(angle = 0))
    e <- tmCA.res$eigvec.plot.r
    f <- tmCA.res$eigvec.plot.c
    g <- tmCA.res$eigval.plot.r
    h <- tmCA.res$eigval.plot.c
    e <- e + inset_element(g, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    f <- f + inset_element(h, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    png(file = here("Plots", "main.png"), width=950, height=1200)
        (a | e | f) / (c | d) / b
    dev.off() 
```

>>>>

# Analysis
```{r Reflections Bump Charts}
   evens <- function(x) subset(x, x %% 2 == 0)
   odds <- function(x) subset(x, x %% 2 != 0)
   a <- reflections(A, iter = 26)
   p.e.r <- a$p.r[, evens(1:20)]
   p.o.r <- a$p.r[, odds(1:20)]
   p.o.r <- p.o.r[, -1]
   b <- ref.long.dat(a = a$p.r, b = a$g.r, max.iter = 26)
   plot.dat <- b$person$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = person))
   # geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 0.8)
   p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = person), 
                                    size = 4, nudge_x = -3)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 22), 
                              aes(x = n.iter, label = person), 
                              size = 4, nudge_x = 0.5)

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- a$A.plot.ca
   c <- a$A.plot.bon
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a")
   dev.off() 
```

```{r Main Plot}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 5, k.c = 5, d.r = 9, d.c = 9)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmCA.res$sim.plot.r + theme(axis.text.x = element_blank())
    f <- tmCA.res$sim.plot.c + theme(axis.text.x = element_blank())
    g <- tmCA.res$corr.plot

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a")
    dev.off()

    png(file = here("Plots", "sim.png"), width=950, height=700)
        (e | f) / g + plot_annotation(tag_levels = "a")
    dev.off() 
```
